High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-01-20 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24. The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around three times the noise in the ALMA image ($\sim1\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$). As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13. Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-size dust of 0.61\,au. The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model. In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au. It contains a total dust mass of $\sim$44\,M$_{\earth}$. The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation. Using the large grains' scale height at Ring13 of 0.61\,au, and a measured width of 2.46\,au, the ring is $\sim$4.1 times more extended radially than vertically.

>>>>

The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24. The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$). This gives us an upper limit for the total millimeter-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$.

As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13. Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-size dust of 0.61\,au. The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model. In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au. It contains a total dust mass of $\sim$44\,M$_{\earth}$. The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation. Using the large grains' scale height at Ring13 of 0.61\,au, and a measured width of 2.46\,au, the ring is $\sim$4.1 times more extended radially than vertically.
